---
title: "assignment start"
author: "Sören Twietmeyer"
date: "`r Sys.Date()`"
output: html_document
---
<style>
body {
text-align: justify}
</style>
# EC349 Assignment 1: Analysis of Yelp Data

## Task outline: 
Predict the rating of user i for business j as the number of stars given
## Project Plan: Outline
1. Business and goal understanding
2. Analytic Approach
+ simple relationships between variables
+ clustering of variables
+ might have to go to data cleaning first and then come back again
3. Data requirements
4. Data preparation


```{r setup, include=FALSE}
library(conflicted)
library(jsonlite)
library(tidyverse)
library(dplyr)
library(tidyr)
library(tm)
library(hexbin)
library(sandwich)
library(lmtest)
library(doParallel)
getwd()
source("../code/assignment_functions.R")
```

```{r Load data}
# Load Different Data
business_data <- stream_in(file("../data/yelp_academic_dataset_business.json"))
business_data_unnested <- unnest(business_data, attributes)
#review_data  <- stream_in(file("../data/yelp_academic_dataset_review.json"))
checkin_data  <- stream_in(file("../data/yelp_academic_dataset_checkin.json"))
#user_data <- stream_in(file("../data/yelp_academic_dataset_user.json"))
tip_data  <- stream_in(file("../data/yelp_academic_dataset_tip.json"))

# Load smaller data sets for comparative purposes and easier testing
load("../data/yelp_review_small.Rda")
load("../data/yelp_user_small.Rda")


```

```{r Data exploration}
# business data
str(business_data_unnested)
empty_rows_business_data <- count_empty_rows(business_data_unnested)
length(unique(business_data_unnested$business_id))

# review data
str(review_data_small)
length(unique(review_data_small$review_id))

# check in data
str(checkin_data)
num_checkins_by_business <- checkin_data  %>% group_by(business_id) %>% summarise(total_checkins = n()) %>% dplyr::filter(total_checkins > 1)

# user data
str(user_data_small)
length(unique(user_data_small$user_id))

str(tip_data)

```
The data exploration phase showed the check in data is not useful for our purpose given the lack of variation in the number of check ins between business. The business data set includes useful information, however, some columns suffer from large shares of missing data, which negatively impacts its usefulness. Having a lot of missing values means that, if we want to include the variables, we need to drop a lot of values, leaving us with too few reviews and probably highly biased results given that the lack of data is probably not random. The tip data only includes additional comments made from a user to a business and can be omitted given the inclusion of the comments of the reviews from the review data set. 

### Data Description
+ data documentation: https://www.yelp.com/dataset/documentation/main
+ review_data: contains review_id, user_id, business_id, stars given to a business(0-5), useful (number of useful votes received), cool (number of cool votes received), funny (number of funny votes received)
+ business_data: location, avg. rating, number of reviews, open/ closed, attributes such as takeout and parking, category i.e. mexican, japanese etc., opening hours
+ user_data: name, friends, review count, number of useful, cool and funny votes **sent** by the user, number of different complements received by different users, avg number of stars given
+ checkin_data: time stamp of check ins made on a business
+ tip_data: comments of users to a particular business, number of compliments each comment received, mapped to user and business

We now need to clean up the data and prepare one dataframe that inlcudes all the necessary information. 
```{r data manipulation}
# review data:
# slice to make testing easier
text_test_df <- review_data_small[1:600000, ]

# Register parallel backend with the number of cores you want to use
cl <- makeCluster(detectCores())
registerDoParallel(cl)

## prepare text for analysis:
corpus <- Corpus(VectorSource(review_data_small$text))

## Preprocess the text: remove punctuation and stopwords
corpus <- tm_map(corpus, tolower)
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeWords, stopwords("english"))
corpus <- tm_map(corpus, stemDocument)

frequencies = DocumentTermMatrix(corpus)
sparse = removeSparseTerms(frequencies, 0.99)
tSparse = as.data.frame(as.matrix(sparse))

# Close the parallel backend
stopCluster(cl)

## we are now left with a matrix that could then be merged onto the other df because the order remains the same, i.e. row order is the same
tSparse$review_id <- review_data_small$review_id

## business data
cols_keep_business_data <- empty_rows_business_data %>% dplyr::filter(`EmptyRows` < 35000 & !Column %in% c('name', 'address', 'latitude', 'longitude'))

## tip data:
num_comments_by_business <- tip_data %>% group_by(business_id) %>% summarise(total_comments_business = n())

# user data:
user_data_selected <- user_data_small  %>% mutate(yelping_since_weeks = round(as.numeric(difftime("2023-12-31 00:00:00", yelping_since, units = "weeks")), digits = 0), num_friends = ifelse(friends != "None", sapply(strsplit(friends, ","), function(x) length(x)), 0), total_compliments = select(., starts_with("compliment_")) %>% rowSums(na.rm = TRUE)) %>% mutate(was_elite = ifelse(nchar(elite) > 1, 1, 0))%>%  select(-c(name, yelping_since, friends, elite))# explain why you aggregated compliments instead of using each individually

# merge other data sets onto review data which is the main one:
review_data_combined <- review_data_small %>% left_join(business_data[, cols_keep_business_data$Column], by = 'business_id', suffix = c('_review', '_business')) %>% left_join(user_data_selected, by = 'user_id', suffix = c('_review', '_user')) %>% left_join(num_comments_by_business, by = 'business_id') %>% left_join(tSparse, by = 'review_id', suffix = c("_review", ""))

# save the dataframe so that we don't have to generate it over and over again
write_csv(review_data_combined, "../data/review_data_combined.csv")

view(count_empty_rows(review_data_combined))

```

```{r further data exploration}
# investigate relationships between different columns and stars_review

# business info:
business_review_comp <- trend_plot("stars_business")

city_plot <- ggplot(review_data_combined %>% group_by(city) %>% summarise(mean_by_city = mean(stars_review)), mapping = aes(x = city, y= mean_by_city)) + geom_col() # clear differences in average ratings by city

state_plot <- ggplot(review_data_combined %>% group_by(state) %>% summarise(mean_by_state = mean(stars_review)), mapping = aes(x = state, y= mean_by_state)) + geom_col() # clear differences in average ratings by state

# review info:
usefulness_info_plot <- ggplot(review_data_combined %>% dplyr::filter(useful_review <300), mapping = aes(x = useful_review, y = stars_review)) + geom_hex() + geom_smooth(method = "glm", formula = y ~ x + x^2 + x^3) + ylim(1,5) ## strong negative correlation

funny_info_plot <- ggplot(review_data_combined %>% dplyr::filter(funny_review <300), mapping = aes(x = funny_review, y = stars_review)) + geom_hex() + geom_smooth(method = "glm", formula = y ~ x + x^2 + x^3) + ylim(1,5) ## strong negative correlation

cool_info_plot <- ggplot(review_data_combined %>% dplyr::filter(cool_review <500), mapping = aes(x = cool_review, y = stars_review)) + geom_hex() + geom_smooth(method = "glm", formula = y ~ x + x^2 + x^3) + ylim(1,5) ## strong positive correlation

review_count_plot <- trend_plot("review_count_review") ## slight positive correlation

# user info: 
friends_count_plot <- trend_plot("num_friends") ## slight positive correlation

fans_count_plot <- trend_plot("fans") ## slight positive correlation

compliments_count_plot <- trend_plot("total_compliments") ## slight positive correlation

yelp_since_plot <- trend_plot("yelping_since_weeks")
```

```{r test and training set generation}
final_dataset <- review_data_combined %>% select(-c("date", "text", starts_with("compliment_")))

#Split data into test and training
set.seed(1)
train <- sample(1:nrow(review_data_combined), nrow(review_data_combined) - 10000) #keep 10,000 for the test data
data_train <-review_data_combined[train,]

#Test data
data_test <- review_data_combined[-train,]

# for shrinkage estimators we need to transform data into matrices, therefore we need the following transformation: 
data_train_x <-data_train[,!colnames(data_test) %in% c("stars_review")]
data_train_y <-data_train[,c("stars_review")]

data_test_x <-data_test[, !colnames(data_test) %in% c("stars_review")]
data_test_y <-data_test[,c("stars_review")]
```

```{r modelling and performance testing}
##Linear Regression Model of stars given for a review as a function of user, business, and review characteristics
lm_stars<- lm(stars_review ~ state + num_friends + total_compliments, data = data_train)

#Review the results
summary(lm_stars)

#Prediction to test data
lm_stars_predict<-predict(lm_cars, newdata = data_test[,!colnames(data_test) %in% c("stars_review")])

#Empirical MSE in TEST data
lm_stars_test_mse<-mean((lm_stars_predict-data_test$stars_review)^2)

coeftest(lm_stars, vcov = vcovHC(lm_stars, type="HC3")) # what is this for? says for robust se

## LASSO and Ridge
ridge_results <- shrinkage_estimator_computation(0, data_train_x, data_train_y, data_test_x, data_test_y)
cv_out_ridge <- ridge_results[[1]]
plot_cv_out_ridge <- ridge_results[[2]]
lambda_ridge_cv<- ridge_results[[3]]
ridge_model<- ridge_results[[4]]
ridge_predictions<- ridge_results[[5]]
ridge_mse <- ridge_results[[6]]


#LASSO with Cross-Validation
lasso_results <- shrinkage_estimator_computation(1, data_train_x, data_train_y, data_test_x, data_test_y)
cv_out_lasso <- lasso_results[[1]]
plot_cv_out_lasso <- lasso_results[[2]]
lambda_lasso_cv<- lasso_results[[3]]
lasso_model<- lasso_results[[4]]
lasso_predictions<- lasso_results[[5]]
lasso_mse <- lasso_results[[6]]

```

```{r model comparison with adapted data}
## Comparison of LASSO and ridge with frequency matrix of words replaced by binary (used/ not used) matrix
adapted_df <- final_dataset %>% mutate_at(vars(colnames(tSparse)), list(~ifelse(. > 0, 1, 0)))
# generate new training and test datasets
data_train_binary <-adapted_df[train,]

#Test data
data_test_binary <- adapted_df[-train,]

# for shrinkage estimators we need to transform data into matrices, therefore we need the following transformation: 
data_train_binary_x <-data_train_binary[,!colnames(data_test_binary) %in% c("stars_review")]
data_train_binary_y <-data_train_binary[,c("stars_review")]

data_test_binary_x <-data_test_binary[, !colnames(data_test_binary) %in% c("stars_review")]
data_test_binary_y <-data_test_binary[,c("stars_review")]

# application on LASSO and Ridge
ridge_results_binary <- shrinkage_estimator_computation(0, data_train_binary_x, data_train_binary_y, data_test_binary_x, data_test_y)
cv_out_ridge_binary <- ridge_results_binary[[1]]
plot_cv_out_ridge_binary <- ridge_results_binary[[2]]
lambda_ridge_cv_binary <- ridge_results_binary[[3]]
ridge_model_binary <- ridge_results_binary[[4]]
ridge_predictions_binary <- ridge_results_binary[[5]]
ridge_mse_binary <- ridge_results_binary[[6]]


#LASSO with Cross-Validation
lasso_results_binary <- shrinkage_estimator_computation(1, data_train_binary_x, data_train_y, data_test_binary_x, data_test_binary_y)
cv_out_lasso_binary <- lasso_results_binary[[1]]
plot_cv_out_lasso_binary <- lasso_results_binary[[2]]
lambda_lasso_cv_binary <- lasso_results_binary[[3]]
lasso_model_binary <- lasso_results_binary[[4]]
lasso_predictions_binary <- lasso_results_binary[[5]]
lasso_mse_binary <- lasso_results_binary[[6]]
```

## Methodology
This data science project requires a methodology that is iterative, intuitive and suitable for an individual project. Therefore, the CRISP-DM methodology is inappropriate given the large amount of documentation and stakeholder involvement included. Both, the SEMMA and OSEMN methods lack a phase dedicated to a clear problem definition. Despite it being an individual project outside a corporate setting, clearly defining the goal is crucial. Additionally, the TDSP and KDD methodologies are similar in structure to the John Rallin DS methodology, however, the latter is more detailed than the TDSP methodology. Thus, I will use an adapted version of the John Rallin general DS methodology. In particular, I will limit the first and last stages given the lack of a real-world setting which would require client and sponsor interaction as well as implementation. 


## Project Challenges

